%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.1 (9/1/2016)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Claud D. Park (posquit0.bj@gmail.com)
% Lars Richter (mail@ayeks.de)
% With modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[8pt, letterpaper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=1.5cm, top=1.5cm, right=1.5cm, bottom=2cm, footskip=.5cm} % Configure page margins with geometry

\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\definecolor{awesome-blue}{HTML}{00274c} % michigan blue
\colorlet{awesome}{awesome-skyblue} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\name{A Lyjak Cybernetics Consulting LLC}{}
\address{46800 Bettyhill, Plymouth MI, 48170} % Your address
\mobile{(+1) (734)604-6163}
%% \homepage{spacelyjak.rtfd.io}
%% \github{alyjak}
%% \linkedin{andrew-lyjak}
%% %\skype{skypeid}
%% %\stackoverflow{SOid}{SOname}
%% \twitter{@spacelyjak}
%% %\linkedin{linkedin name}
%% %\reddit{reddit account}
%% %\xing{xing name}
\email{andrew.lyjak@gmail.com}
%\extrainfo{test} % Other text you want to include on this line

%% \position{Software Development and Verification{\enskip\cdotp\enskip}Systems Engineer} % Your expertise/fields
%% \quote{``This is the real secret of life -- to be completely engaged
%%   with what you are doing in the here and now. And instead of calling
%%   it work, realize it is play.''} % Alan Watts

\makecvfooter{}{A Lyjak Cybernetics Consulting LLC}{} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed

%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------

\recipient{}{H3D, Inc\\https://h3dgamma.com}

\letterdate{\today} % The date on the letter, default is the date of compilation

\lettertitle{Letter of Commitment} % The title of the letter

\letteropening{Dear H3D Inc,} % How the letter is opened

\letterclosing{Sincerely,} % How the letter is closed

%\letterenclosure[Attached]{}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header

\makelettertitle % Print the title

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\begin{cvletter}
  A Lyjak Cybernetics Consulting LLC's (ALCC) is commited to supporting H3D, Inc.\ through execution
  of the tasks outlined in Appendix A of the consulting agreement initially signed by myself on
  3/27/2023 and by Michael Streicher on 4/6/2023. The agreement was amended and re-signed by myself
  on 8/16/2023 and by Michael Streicher on 8/29/2023. It is our joint understanding that execution
  of this contract will benefit the efficiency and quality of H3D's production and product
  development capacities. This contract is a fixed price contract. The price of each task is
  calculated based on the task's work-hour estimate multiplied by ALCC's standard hourly rate of
  \letternamestyle{\$120/hr} It is my understanding that H3D depends on A Lyjak Cybernetics
  Consulting LLC fully and faithfully executing the statement of work as part of the general work
  and cost associated with H3D's effort towards ``FY25 DOE Phase I SBIR Proposals``. All costs
  associated with this contract are labor costs. We confirm that the rates used on for this contract
  are consistent with ALCC's standard prices. There are no parts, equipment, or materials billed
  under the contract. All tasks are to be billed in the second budget year. The following is a
  summary of the contracted tasks and their prices:

  \begin{description}
    \item[Warranty Data] Integrate Customer Warranty data from an external enterprise system into
      H3ID. Warranty information will inform what the newest update patch the customer is entitled
      to as a suggestion for patch to apply. \letternamestyle{Effort: 24 work-hours,
      Price: \$2,880.00}

    \item[Upgrade Production Server] Migrate the production H3ID service to the latest release of
      H3ID. This task includes updating the OS and service dependencies to the latest stable
      versions as well as system testing prior to the final migration. \letternamestyle{Effort: 24
        work-hours, Price: \$2,880.00}

    \item[Upgrade Local Network Detector Discovery] H3D recently installed a new local network
      firewall. Investigate whether the firewall supports ipv6 multicast and if so, enable a more
      efficient detector discovery process than the ip address polling currently in
      practice. \letternamestyle{Effort: 8 work-hours, Price: \$960.00}

    \item[Manage multi-headed detectors as an integrated assembly] Enable programming/configuration
      of multi-headed detectors both as individual heads as well as the full assembly. Create a UI
      for joining heads into a multi-headed detector and batch configuring
      them. \letternamestyle{Effort: 24 work-hours, Price: \$2,880.00}

    \item[Customer Feedback UI fixes] Misc UI fixes informed by H3D Production specialist's feedback
      on the service. \letternamestyle{Effort: 6 work-hours, Price: \$720.00}

    \item[Create Design Proposal for integrating H3ID and Fishbowl production workflows] Work with
      stakeholders to create process and workflow diagrams to understand how H3ID should optimally
      integrate with FishBowl. After design consultation and design review of the vision, create a
      statement of work for the necessary implementation and testing to achieve the agreed upon
      design. \letternamestyle{Effort: 24 work-hours, Price: \$2,880.00}

    \item[Total Contract Value] \letternamestyle{Effort: 110 work-hours, Price: \$13,200.00}

  \end{description}

  In conclusion, A Lyjak Cybernetics Consulting LLC is fully committed to fully and faithfully
  executing this contract. \\

\end{cvletter}
\lettertextstyle{Sincerely,} \\\\\\\\\\
\letternamestyle{Andrew\ Lyjak} \\
\lettertextstyle{owner}
% \newpage
%\makecvheader % Print the header

%----------------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%----------------------------------------------------------------------------------------

% \makecvheader % Print the header

%% \input{cv-sections/education.tex}
%% \input{cv-sections/skills.tex}
%% \input{cv-sections/experience.tex}
%% \input{cv-sections/extracurricular.tex}

\end{document}
