%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.1 (9/1/2016)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Claud D. Park (posquit0.bj@gmail.com)
% Lars Richter (mail@ayeks.de)
% With modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[8pt, letterpaper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=1.5cm, top=1.5cm, right=1.5cm, bottom=2cm, footskip=.5cm} % Configure page margins with geometry

\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\definecolor{awesome-blue}{HTML}{00274c} % michigan blue
\colorlet{awesome}{awesome-skyblue} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\name{A Lyjak Cybernetics Consulting LLC}{}
\address{46800 Bettyhill, Plymouth MI, 48170} % Your address
\mobile{(+1) (734)604-6163}
%% \homepage{spacelyjak.rtfd.io}
%% \github{alyjak}
%% \linkedin{andrew-lyjak}
%% %\skype{skypeid}
%% %\stackoverflow{SOid}{SOname}
%% \twitter{@spacelyjak}
%% %\linkedin{linkedin name}
%% %\reddit{reddit account}
%% %\xing{xing name}
\email{andrew.lyjak@gmail.com}
%\extrainfo{test} % Other text you want to include on this line

%% \position{Software Development and Verification{\enskip\cdotp\enskip}Systems Engineer} % Your expertise/fields
%% \quote{``This is the real secret of life -- to be completely engaged
%%   with what you are doing in the here and now. And instead of calling
%%   it work, realize it is play.''} % Alan Watts

\makecvfooter{}{A Lyjak Cybernetics Consulting LLC}{} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed

%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------

\recipient{}{H3D, Inc\\https://h3dgamma.com}

\letterdate{\today} % The date on the letter, default is the date of compilation

\lettertitle{Letter of Commitment} % The title of the letter

\letteropening{Dear H3D Inc,} % How the letter is opened

\letterclosing{Sincerely,} % How the letter is closed

%\letterenclosure[Attached]{}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header

\makelettertitle % Print the title

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\begin{cvletter}
  A Lyjak Cybernetics Consulting LLC's (ALCC) is commited to supporting H3D,
  Inc.\ through execution of the tasks outlined in Appendix A of the consulting agreement initially
  signed by myself on 3/27/2023 and by Michael Streicher on 4/6/2023. The agreement was amended and
  re-signed by myself on 8/16/2023 and by Michael Streicher on 8/29/2023. It is our joint
  understanding that execution of this contract will benefit the efficiency and quality of H3D's
  production and product development capacities. This contract is a fixed price contract. The price
  of each task is calculated based on the task's work-hour estimate multiplied by ALCC's standard
  hourly rate of \letternamestyle{\$120/hr} It is my understanding that H3D depends on A Lyjak
  Cybernetics Consulting LLC fully and faithfully executing the statement of work as part of the
  general work and cost associated with H3D's development effort entitled ``High Signal-to-Noise
  Pixelated CZT Directional Spectrometer for Generalized Holdup Measurements''. All costs associated
  with this contract are labor costs. We confirm that the rates used on for this contract are
  consistent with ALCC's standard prices. There are no parts, equipment, or materials billed under
  the contract. All tasks are to be billed in the second budget year. The following is a summary of
  the contracted tasks and their prices:

  \begin{description}
    \item[Detector QC Configuration and Verification] This task is focused on ensuring H3D is using
      the full capabilities of the detector burner and updater. The main focus is ensuring
      configuration file templates are produced correctly and the operator is aware and in-control
      of what is going on during an image burn/update. \letternamestyle{Effort: 27 work-hours,
      Price: \$3,240.00}

    \item[Extract Open Source Software from H3ID] Extract base software and configuration-as-code
      infrastructure from H3ID, H3D's in-house product lifecycle management (PLM) application suite,
      into a separate open source project. We predict this task to increase the reliability, and
      lower the per-user cost for the PLM application by increasing the available pool of users and
      developers using the product. \letternamestyle{Effort: 88 work-hours, Price: \$10,560.00}

    \item[Capture Calibration Data and Store in H3ID] Define and implement a schema and associated
      API functionality that delineates calibration data from other system configuration
      information. This functionality will enable product lifecycle-aware application and extraction
      of calibration data to and from system configuration files. \letternamestyle{Effort: 68
        work-hours, Price: \$8,160.00}

    \item[Golden Archive Rendered Template Override] This milestone is complete Add a field to burn
      logs that allows them to be flagged as a golden archive. If a golden archive is flagged for a
      particular detector, then do not render templates, instead populate the staging filesystem
      with the files within/linked to the archive. Then when synchronizing filesystems, this will
      enable the user to view differences between the detector's filesystem and the archive, rather
      than between the detector and the rendered templates. Only allow one golden archive per
      detector. \letternamestyle{Effort: 16 work-hours, Price: \$1920.00}


    \item[Update Production Server] Run the update server procedure, ensuring to push new defaults
      (calibration key schema files), and create and save new migrations. \letternamestyle{Effort: 8
      work-hours, Price: \$960.00}

    \item[Total Contract Value] \letternamestyle{Effort: 207 work-hours, Price: \$24,840.00}

  \end{description}

  In conclusion, A Lyjak Cybernetics Consulting LLC is fully committed to fully and faithfully
  executing this contract. \\

\end{cvletter}
\lettertextstyle{Sincerely,} \\\\\\\\\\
\letternamestyle{Andrew\ Lyjak} \\
\lettertextstyle{owner}
% \newpage
%\makecvheader % Print the header

%----------------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%----------------------------------------------------------------------------------------

% \makecvheader % Print the header

%% \input{cv-sections/education.tex}
%% \input{cv-sections/skills.tex}
%% \input{cv-sections/experience.tex}
%% \input{cv-sections/extracurricular.tex}

\end{document}
