\begin{cvletter}

%------------------------------------------------

\lettersection{Introduction}
Dear Angie's List/HomeAdvisor recruitment team,

I recently moved to Indianapolis after living and working in Los Angeles for
over eight years. During this time, I have been employed by SpaceX. Currently
I'm performing my job remotely from my home office in Indianapolis, but I am
looking to move on, and searching for new adventures in an exciting, technology
driven company local to this city.

My interests revolve around bridging the digital and physical world in ways that
are intuitive and safe. At SpaceX, I implement and execute software assurance
activities related to ensuring the safety and quality of flight software for the
Falcon and Dragon vehicles. In this position I have designed and executed
multiple software test and automation projects. In addition I have extensive
experience in the ``soft'' engineering fields such as process, quality, and
requirements engineering.

Additionally, I have had numerous opportunities to collaborate with my wife on
machine learning problems and their solutions related to her work as a
neuroscientist specializing in studying imaging and genetics related to the
understanding of Alzheimer's disease. This is how I have developed proficiency
with R, machine learning, and data analysis.


%------------------------------------------------

\lettersection{Why Angie's List/HomeAdvisor?}

I am very motivated by improving local communities through technology. I believe
that Angie's List/HomeAdvisor aligns with my values. Helping to nurture local
businesses and while providing value and trust to local customers is more than a
job to me, it's a mission. Too often technology disconnects us from our local
communities, Angie's List/HomeAdvisor provides a refreshing reversal of this
paradigm.


%------------------------------------------------

\lettersection{Why Me?}

My background in aerospace engineering should prove my technical acumen, while
my broad range of experience at SpaceX should prove my capability, self
motivation, and ability to quickly learn on the job. I pride myself in basing my
work on first principles, this helps maintain focus on the right solution, not
just what is currently popular or hyped. I believe I have established a
reputation for being reliable, and a valued and respected member of each team I
have had the pleasure of working with. I look forward to having further
conversations with the Angie's List and HomeAdvisor team!

%------------------------------------------------

\end{cvletter}

%----------------------------------------------------------------------------------------
