\begin{cvletter}

\lettersection{Introduction}
Dear ClearObject recruitment team,

I recently moved with my wife to the Indianapolis area after working
for SpaceX in Los Angeles for eight years. I am currently working
remotely for SpaceX, but I am looking for new adventures in an
exciting, technology driven company.

My interests revolve around bridging the digital and physical world in
ways that are intuitive and safe. At SpaceX, I implement and execute
software assurance activities related to ensuring the safety and
quality of flight software for the F9 and Dragon vehicles. In this
position I have gathered and maintained experience in a diverse range
of engineering fields: examples include the ``hard'' engineering
fields such as aerospace, electrical, and computer engineering, as
well as the ``soft'' engineering fields such as process, quality, and
requirements engineering.


%------------------------------------------------

\lettersection{Why ClearObject?}

Internet of Things interest me greatly -- because of both its promise
as well as its pitfalls. IOT promises to provide new capabilities and
connectivity to consumers and businesses, its pitfalls are avoidable,
and mainly revolve around the problems an insecurely connected world
entails. I am looking for exiting opportunities at the forefront of
this burgeoning industry in Indianapolis. I find ClearObject
particularly exciting because of the respect you have in the local
community, the strength of your services, and your focus on the
platforms underlying IOT progress.

%------------------------------------------------

\lettersection{Why Me?}

I believe my diverse range of skills is ideal for your Software Test
Engineer position. In addition, my skills make me a promising
candidate for your full stack developer position. Through SpaceX, I
have experience in each role and responsibility identified within the
Software Test Engineer job posting. Although I have an Aerospace
degree, I have worked in Computer Engineering/Science fields both
within college and through my eight years at SpaceX. I have
demonstrated my ability to learn new material quickly and efficiently
and I am known to be self-driven and to enjoy solving challenging
problems. I pride myself in basing my work on principles, this helps
maintain focus on the right solution, not just what is currently
popular or hyped. I believe I have established a reputation for being
reliable and a valued and respected member of each team I have had the
pleasure of working with.

%------------------------------------------------

\end{cvletter}
