%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.1 (9/1/2016)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Claud D. Park (posquit0.bj@gmail.com)
% Lars Richter (mail@ayeks.de)
% With modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm} % Configure page margins with geometry
 
\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\definecolor{awesome-blue}{HTML}{00274c} % michigan blue
\colorlet{awesome}{awesome-skyblue} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\name{Andrew W.}{Lyjak}
\address{6205 N Oakland Ave, Indianapolis IN, 46220} % Your address
\mobile{(+1) (734)604-6163}

\email{andrew.lyjak@gmail.com}
\homepage{spacelyjak.rtfd.io}
\github{alyjak}
\linkedin{andrew-lyjak}
%\skype{skypeid}
%\stackoverflow{SOid}{SOname}
\twitter{@spacelyjak}
%\linkedin{linkedin name}
%\reddit{reddit account}
%\xing{xing name}
%\extrainfo{test} % Other text you want to include on this line

\position{Software Assurance/Verification/Development{\enskip\cdotp\enskip}Systems Engineer} % Your expertise/fields
% \quote{``This is the real secret of life -- to be completely engaged
%   with what you are doing in the here and now. And instead of calling
%   it work, realize it is play.''} % Alan Watts

%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------

\recipient{Company Recruitment Team}{ClearObject\\8627 East 116th
  Street, Suite 300\\Fishers, IN 46038} % The company being applied to

\letterdate{\today} % The date on the letter, default is the date of compilation

\lettertitle{Job Application for Software Test Engineer or Full Stack Developer} % The title of the letter

\letteropening{To whom it may concern,} % How the letter is opened

\letterclosing{Sincerely,} % How the letter is closed

%\letterenclosure[Attached]{}

\makecvfooter{\today}{Andrew W. Lyjak~~~·~~~Cover Letter}{} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed

%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header

\makelettertitle % Print the title

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\begin{cvletter}

%------------------------------------------------

\lettersection{About Me}

I recently moved with my wife to the Indianapolis area after working
for SpaceX in Los Angeles for eight years. I am currently working
remotely for SpaceX, but I am looking for new adventures in an
exciting, technology driven company.

My interests revolve around bridging the digital and physical world in
ways that are intuitive and safe. At SpaceX, I implement and execute
software assurance activities related to ensuring the safety and
quality of flight software for the F9 and Dragon vehicles. In this
position I have gathered and maintained experience in a diverse range
of engineering fields: examples include the ``hard'' engineering
fields such as aerospace, electrical, and computer engineering, as
well as the ``soft'' engineering fields such as process, quality, and
requirements engineering.


%------------------------------------------------

\lettersection{Why ClearObject?}

Internet of Things interest me greatly -- because of both its promise
as well as its pitfalls. IOT promises to provide new capabilities and
connectivity to consumers and businesses, its pitfalls are avoidable,
and mainly revolve around the problems an insecurely connected world
entails. I am looking for exiting opportunities at the forefront of
this burgeoning industry in Indianapolis. I find ClearObject
particularly exciting because of the respect you have in the local
community, the strength of your services, and your focus on the
platforms underlying IOT progress.

%------------------------------------------------

\lettersection{Why Me?}

I believe my diverse range of skills is ideal for your Software Test
Engineer position. In addition, my skills make me a promising
candidate for your full stack developer position. Through SpaceX, I
have experience in each role and responsibility identified within the
Software Test Engineer job posting. Although I have an Aerospace
degree, I have worked in Computer Engineering/Science fields both
within college and through my eight years at SpaceX. I have
demonstrated my ability to learn new material quickly and efficiently
and I am known to be self-driven and to enjoy solving challenging
problems. I pride myself in basing my work on principles, this helps
maintain focus on the right solution, not just what is currently
popular or hyped. I believe I have established a reputation for being
reliable and a valued and respected member of each team I have had the
pleasure of working with.

%------------------------------------------------

\end{cvletter}

%----------------------------------------------------------------------------------------

\makeletterclosing % Print the signature and enclosures

\end{document}