\begin{cvletter}

%------------------------------------------------

\lettersection{Introduction}
Dear Onebridge recruitment team,

I recently moved to Indianapolis after living and working in Los Angeles for
over eight years. During this time, I have been employed by SpaceX. Currently
I'm performing my job remotely from my home office in Indianapolis, but I am
looking to move on, and searching for new adventures in an exciting, technology
driven company local to this city.

My interests revolve around bridging the digital and physical world in ways that
are intuitive and safe. At SpaceX, I implement and execute software assurance
activities related to ensuring the safety and quality of flight software for the
Falcon and Dragon vehicles. In this position I have gathered and maintained
experience in a diverse range of engineering fields: examples include the
``hard'' engineering fields such as aerospace, electrical, and computer
engineering, as well as the ``soft'' engineering fields such as process,
quality, and requirements engineering.

Additionally, I have had numerous opportunities to collaborate with my wife on
machine learning problems and their solutions related to her work as a
neuroscientist specializing in studying imaging and genetics related to the
understanding of Alzheimer's disease. This is how I have developed proficiency
with R, specifically associated with its tremendous capabilities in the fields
of machine learning and data analysis.


%------------------------------------------------

\lettersection{Why Onebridge?}

I had the opportunity to visit Onebridge as part of an R meetup in September and
was very impressed with the personnel I met. Specifically, Bill McLellan's talk
about his experience with igraph was quite engaging. From my quick tour, the
company seems driven and sincere in their desire to solve some of the trickier
problems facing their customers. In addition the breadth of skills fostered
within Onebridge is very intriguing to me. As I hope you can see in my resume, I
share many of the same interests and skill sets that the company fosters.


%------------------------------------------------

\lettersection{Why Me?}

The skill set maintained by the Onebridge team -- specifically the combination
of analysis, application development, quality, and IT maintenance roles --
applies very well to my skill set. My background in aerospace engineering should
prove my technical acumen, while my broad range of experience at SpaceX should
prove my capability, and self motivation. I pride myself in basing my work on
first principles, this helps maintain focus on the right solution, not just what
is currently popular or hyped. I believe I have established a reputation for
being reliable and a valued and respected member of each team I have had the
pleasure of working with. I look forward to having further conversations with
the Onebridge team!

%------------------------------------------------

\end{cvletter}

%----------------------------------------------------------------------------------------
