\begin{cvletter}

%------------------------------------------------

\lettersection{Introduction}
Dear Bloomerang recruitment team,

I recently moved to Indianapolis after living and working in Los Angeles for over eight
years. During this time, I was employed by SpaceX. After moving to Indy, I worked remotely for
SpaceX on a temporary contract, which was recently completed (Dec 2018). I am looking to move on
from the aerospace industry, and I'm searching for new adventures in a mission-driven company local
to this city.

My interests revolve around bridging the digital and physical world in ways that are intuitive and
safe. At SpaceX, I implemented and executed software assurance activities related to ensuring the
safety and quality of flight software for the Falcon and Dragon vehicles. In this position I
gathered and maintained experience in a diverse range of engineering fields: examples include the
``hard'' engineering fields such as aerospace, electrical, and computer engineering, as well as the
``soft'' engineering fields such as process, quality, and requirements engineering.

Additionally, I have had numerous opportunities to collaborate with my wife on machine learning
problems and their solutions related to her work as a neuroscientist specializing in studying
imaging and genetics related to the understanding of Alzheimer's disease. This is how I have
developed proficiency with R, specifically associated with its tremendous capabilities in the fields
of machine learning and data analysis.


%------------------------------------------------

% \lettersection{Why Ice Miller?}

% Many of the hard and interesting problems I work on at SpaceX involve the
% intersection of regulation and data interpretation. Having the opportunity to
% further explore this area of my experience intersts me greatly. I believe that
% technology has not achieved its potential for empowering decision makers who
% need to quickly interpret data and regulations in order to understand the
% salient points of their cases. I would love to further explore this area with
% the Ice Miller firm, and I believe the Application Data Analyst position is
% perfect do this.

%------------------------------------------------

\lettersection{Why Me?}

My background in aerospace engineering should prove my technical and analytical acumen, while my
broad range of software experience at SpaceX should prove my broad skill set, self motivation, and
ability to quickly learn on the job. I pride myself in basing my work on first principles, this
helps maintain focus on the right solution, not just what is currently popular or hyped. I believe I
have established a reputation for being a reliable, valued, and respected member of each team I have
had the pleasure of working with. I look forward to having further conversations with the Bloomerang
team!

%------------------------------------------------

\end{cvletter}

%----------------------------------------------------------------------------------------
