\begin{cvletter}

%------------------------------------------------

% \lettersection{Introduction}
Early in my career I realized that a person's decision making quality can be improved by changing
their environment. Helping to create environments that improve the quality of thought has been my
calling ever since. Now that I have children, this interest has grown and blossomed. I am no longer solely
focused on workplace environments but rather on what interventions might help individuals
society-wide. I am enthusiastic about the mission of Verses, and I believe that my skills,
interests, and experience could be a valuable asset to the company.

As you can see from my résumé, my experience is fairly diverse yet shares a common theme -- my
projects involve designing systems to improve decision-making. I have worked as a team as well as
independently to design, implement, and validate projects of various scales. I am keenly interested
in how to design environments in order to encourage effective coordination and high quality decision
making.

At SpaceX, I coordinated, implemented, and executed projects and activities related to ensuring the
safety and quality of mission-critical software. I developed expertise in a wide range of topics,
including ``hard science'' fields such as aerospace, electrical, and computer engineering, as well
as ``soft science'' fields. One of the most important lessons I learned at SpaceX is the importance
of pragmatism and the ability to perform effective product-feature triage. When creating a product,
it is much more to plan on continuous improvement than on perfection. The fastest way to improve,
both personally and product-wise, is to keep executing. Post-SpaceX, I have used my experience to
design and implement engineering coordination systems, including a continuous integration platform
for Raytheon, and a production workflow platform for my last salaried employer, H3D. Presently, I am
developing a Production Lifecycle Management application that shares a similar vision to that
espoused by Verses through products such as KOSM that are oriented towards inclusive collaboration
between artificial and human systems. Verses interest in sense-making, distributed intelligence, and
first-principles R\&D and engineering resonates strongly with my interests.

I would also like to note that my wife, Dr. Brandalyn Riedel, has provided me with a range of skills
I would otherwise not have had the opportunity to develop. Not only has her background in psychology
and her PhD in Neuroscience deepened my understanding of what works and what doesn't with respect to
the mind and learning, but I have also been able to collaborate with her on statistics and machine
learning problems. This skillset will prove useful for work at Verses.

In closing, my background, skills, and motivations seem well suited to helping Verses succeed. I,
and my family, are enthusiastic about the opportunity to join you in your quest to reimagine the
relationship between AGI/ASI technologies and humanity through leveraging lessons from physics-based
first principles while staying grounded in ethics. I have submitted my application for more than one
job posting, as I believe I could excel in a few different positions. Thank you for reviewing my
application and I hope to hear from you soon.

%------------------------------------------------

\end{cvletter}

%----------------------------------------------------------------------------------------
